### 2021-10-07 paper/output/document/paper41.tex
at least it's consistent

While Kitcher's conception of a maxim captures Kant's idea of acting for duty's own sake, I will not implement it 
because it is not necessary for putting maxims through the FUL. Indeed, Kitcher acknowledges that 
O'Neill's formulation suffices for the universalizability test, but is not the general notion of a maxim.
In order to pass the maxim through the FUL, it suffices to know the circumstance, act, and goal. The FUL
derives the motive that Kitcher bundles into the maxim, so automating the FUL does not require 
including a motive. The ``input" to the FUL is the circumstance, act, goal pair. My project takes 
this input and returns the motivation that the dutiful, moral agent would adopt. Additionally, doing
justice to the rich notion of motive requires modelling the operation of practical reason itself, 
which is outside the scope of this project. My work focuses on the universalizability test, but future work that 
models the process of practical reason may use my implementation of the FUL as a ``library." Combined 
with a logic of practical reason, an implementation of the FUL can move from evaluating a maxim to 
evaluating an agent's behavior, since that's when ``acting from duty" starts to matter.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{fun}\isamarkupfalse%
\ will\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim\ {\isasymRightarrow}\ s{\isasymRightarrow}\ \ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}A\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}will\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharequal}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
Korsgaard claims that ``to will an end, rather than just
wishing for it or wanting it, is to set yourself to be its cause" \cite{sources}. To will a maxim, then, 
is to set yourself to, in the relevant circumstances, be the cause of its goal by taking the means 
specified in the maxim. This coheres with 
Kitcher's and Korsgaard's understanding of a maxim as a principle or rule to live by. At worlds 
where the circumstances do not hold, a maxim is vacuously willed. If you decide to act on the rule ``I will 
do X in these cirumstances", then you are vacuously obeying it when the circumstances don't hold.

@@

If the circumstances do not hold and the goal is achieved, then the maxim is vacuously effective, since 
it is vacuously willed (as described above). While this scenario is counterintuitive, it is not very 
interesting for my purposes because, when the circumstances do not hold, a maxim is not applicable. It 
doesn't really make sense to evaluate a maxim when it's not supposed to be applied. The maxim ``When on Jupiter,
read a book to one-up your nemesis" is vacuously effective because it can never be disproven.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/paper41.thy%:%
%:%24=6%:%
%:%36=8%:%
%:%37=9%:%
%:%46=11%:%
%:%58=13%:%
%:%59=14%:%
%:%60=15%:%
%:%61=16%:%
%:%62=17%:%
%:%63=18%:%
%:%65=20%:%
%:%66=20%:%
%:%67=20%:%
%:%68=20%:%
%:%69=21%:%
%:%70=21%:%
%:%71=21%:%
%:%72=21%:%
%:%73=22%:%
%:%74=23%:%
%:%75=23%:%
%:%76=23%:%
%:%77=24%:%
%:%78=25%:%
%:%79=26%:%
%:%80=27%:%
%:%81=28%:%
%:%82=29%:%
%:%83=30%:%
%:%86=32%:%
%:%87=33%:%
%:%88=34%:%
%:%89=35%:%
%:%90=36%:%
%:%91=37%:%
%:%92=38%:%
%:%93=39%:%
%:%94=40%:%
%:%95=41%:%
%:%96=42%:%
%:%97=43%:%
%:%98=44%:%
%:%99=45%:%
%:%100=46%:%
%:%101=47%:%
%:%102=48%:%
%:%103=49%:%
%:%104=50%:%
%:%105=51%:%
%:%106=52%:%
%:%107=53%:%
%:%108=54%:%
%:%109=55%:%
%:%110=56%:%
%:%111=57%:%
%:%112=58%:%
%:%113=59%:%
%:%114=60%:%
%:%115=61%:%
%:%116=62%:%
%:%117=63%:%
%:%118=64%:%
%:%119=65%:%
%:%120=66%:%
%:%121=67%:%
%:%122=68%:%
%:%123=69%:%
%:%124=70%:%
%:%125=71%:%
%:%126=72%:%
%:%127=73%:%
%:%128=74%:%
%:%129=75%:%
%:%130=76%:%
%:%131=77%:%
%:%132=78%:%
%:%133=79%:%
%:%134=80%:%
%:%135=81%:%
%:%136=82%:%
%:%137=83%:%
%:%138=84%:%
%:%139=85%:%
%:%140=86%:%
%:%141=87%:%
%:%142=88%:%
%:%143=89%:%
%:%144=90%:%
%:%145=91%:%
%:%146=92%:%
%:%147=93%:%
%:%148=94%:%
%:%149=95%:%
%:%150=96%:%
%:%151=97%:%
%:%152=98%:%
%:%153=99%:%
%:%154=100%:%
%:%155=101%:%
%:%156=102%:%
%:%157=103%:%
%:%158=104%:%
%:%159=105%:%
%:%160=106%:%
%:%161=107%:%
%:%162=108%:%
%:%163=109%:%
%:%164=110%:%
%:%165=111%:%
%:%166=112%:%
%:%167=113%:%
%:%168=114%:%
%:%169=115%:%
%:%170=116%:%
%:%171=117%:%
%:%172=118%:%
%:%173=119%:%
%:%174=120%:%
%:%175=121%:%
%:%176=122%:%
%:%177=123%:%
%:%179=125%:%
%:%180=125%:%
%:%181=126%:%
%:%183=128%:%
%:%184=129%:%
%:%185=130%:%
%:%186=131%:%
%:%187=132%:%
%:%188=133%:%
%:%189=134%:%
%:%190=135%:%
%:%191=136%:%
%:%192=137%:%
%:%193=138%:%
%:%194=139%:%
%:%195=140%:%
%:%196=141%:%
%:%197=142%:%
%:%198=143%:%
%:%199=144%:%
%:%200=145%:%
%:%201=146%:%
%:%202=147%:%
%:%203=148%:%
%:%204=149%:%
%:%205=150%:%
%:%206=151%:%
%:%207=152%:%
%:%208=153%:%
%:%209=154%:%
%:%210=155%:%
%:%211=156%:%
%:%212=157%:%
%:%213=158%:%
%:%214=159%:%
%:%215=160%:%
%:%216=161%:%
%:%217=162%:%
%:%218=163%:%
%:%219=164%:%
%:%220=165%:%
%:%221=166%:%
%:%222=167%:%
%:%223=168%:%
%:%224=169%:%
%:%226=172%:%
%:%227=172%:%
%:%228=173%:%
%:%230=175%:%
%:%231=176%:%
%:%232=177%:%
%:%233=178%:%
%:%234=179%:%
%:%235=180%:%
%:%236=181%:%
%:%237=182%:%
%:%238=183%:%
%:%239=184%:%
%:%240=185%:%
%:%241=186%:%
%:%242=187%:%
%:%243=188%:%
%:%244=189%:%
%:%245=190%:%
%:%246=191%:%
%:%247=192%:%
%:%248=193%:%
%:%249=194%:%
%:%250=195%:%

>>>>

While Kitcher's conception of a maxim captures Kant's idea of acting for duty's own sake, I will not implement it 
because it is not necessary for putting maxims through the FUL. Indeed, Kitcher acknowledges that 
O'Neill's formulation suffices for the universalizability test, but is not the general notion of a maxim.
In order to pass the maxim through the FUL, it suffices to know the circumstance, act, and goal. The FUL
derives the motive that Kitcher bundles into the maxim, so automating the FUL does not require 
including a motive. The ``input" to the FUL is the circumstance, act, goal pair. My project takes 
this input and returns the motivation that the dutiful, moral agent would adopt. Additionally, doing
justice to the rich notion of motive requires modelling the operation of practical reason itself, 
which is outside the scope of this project. My work focuses on the universalizability test, but future work that 
models the process of practical reason may use my implementation of the FUL as a ``library." Combined 
with a logic of practical reason, an implementation of the FUL can move from evaluating a maxim to 
evaluating an agent's behavior, since that's when ``acting from duty" starts to matter.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{fun}\isamarkupfalse%
\ will\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim\ {\isasymRightarrow}\ s{\isasymRightarrow}\ \ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}W\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}will\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharequal}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
Korsgaard claims that ``to will an end, rather than just
wishing for it or wanting it, is to set yourself to be its cause" \cite{sources}. To will a maxim, then, 
is to set yourself to, in the relevant circumstances, be the cause of its goal by taking the means 
specified in the maxim. This coheres with 
Kitcher's and Korsgaard's understanding of a maxim as a principle or rule to live by. At worlds 
where the circumstances do not hold, a maxim is vacuously willed. If you decide to act on the rule ``I will 
do X in these cirumstances", then you are vacuously obeying it when the circumstances don't hold.

@@

If the circumstances do not hold and the goal is achieved, then the maxim is vacuously effective, since 
it is vacuously willed (as described above). While this scenario is counterintuitive, it is not very 
interesting for my purposes because, when the circumstances do not hold, a maxim is not applicable. It 
doesn't really make sense to evaluate a maxim when it's not supposed to be applied. The maxim ``When on Jupiter,
read a book to one-up your nemesis" is vacuously effective because it can never be disproven.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{fun}\isamarkupfalse%
\ not{\isacharunderscore}universalizable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}not{\isacharunderscore}universalizable\ M\ s\ {\isacharequal}\ {\isacharparenleft}{\isasymTurnstile}\ {\isacharparenleft}{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}p{\isachardot}\ W\ M\ p\ w{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}E\ M\ s{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{The maxim willed by subject $s$ is not universalizable if, for all people $p$, if $p$ wills M, then 
$M$ is no longer effective for $s$.%
}%
\begin{isamarkuptext}%
This formalizes Korgsaard's definition of the practical contradiction
interpretation:  a maxim is not universalizable 
if, in the world where the maxim becomes the standard practice (i.e. everyone acts on the maxim), the
agent's attempt to use the maxim's act to achieve the maxim's goal is frustrated. In other words, if 
the maxim is universally willed (captured by applying a universal qunatifier and the will function 
to the maxim on the LHS), then it is no longer effective for the subject $s$ (RHS above).

One worry is the order of the universal quantifier and the $\vDash$ or derivability symbol. In this 
representation, the universal quantifier is tightly bound to the left hand side of the equation, so it 
only quantifies into the statement ``All p will maxim M at any world." We can imagine an alternate
representation that quantifies over the sentence $\vDash W M p \longrightarrow \sim E M s$. This is 
a sentence of type $s \longrightarrow bool$, since it accepts a subject ($p$) as input and returns 
a boolean (the result of $p$ substituted into the sentence.) Thus, applying the universal quantifier 
$\forall p$ to this sentence results in a boolean that tracks the universalizability (or lack thereof) 
of the maxim. I chose my representation because it tracks the intuitive meaning of the universalizability 
test better: ``IF (the maxim is universalized) THEN (it is no longer effective)".

It's not clear to me if there's any intuitive difference between these two representations, but the lemmas 
below (using simplified versions of the representations) show that my representation is weaker than 
the representation where the quantifier has larger scope. This seems promising—the representation in 
lemma test\_2 is likely too strong because the quantifier quantifies into $M a$ as well. It really 
doesn't seem like this should make a difference, since $p$ never appears on the RHS expression. Let's
see if Prof. Amin has insight.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/paper41.thy%:%
%:%24=6%:%
%:%36=8%:%
%:%37=9%:%
%:%46=11%:%
%:%58=13%:%
%:%59=14%:%
%:%60=15%:%
%:%61=16%:%
%:%62=17%:%
%:%63=18%:%
%:%65=20%:%
%:%66=20%:%
%:%67=20%:%
%:%68=20%:%
%:%69=21%:%
%:%70=21%:%
%:%71=21%:%
%:%72=21%:%
%:%73=22%:%
%:%74=23%:%
%:%75=23%:%
%:%76=23%:%
%:%77=24%:%
%:%78=25%:%
%:%79=26%:%
%:%80=27%:%
%:%81=28%:%
%:%82=29%:%
%:%83=30%:%
%:%86=32%:%
%:%87=33%:%
%:%88=34%:%
%:%89=35%:%
%:%90=36%:%
%:%91=37%:%
%:%92=38%:%
%:%93=39%:%
%:%94=40%:%
%:%95=41%:%
%:%96=42%:%
%:%97=43%:%
%:%98=44%:%
%:%99=45%:%
%:%100=46%:%
%:%101=47%:%
%:%102=48%:%
%:%103=49%:%
%:%104=50%:%
%:%105=51%:%
%:%106=52%:%
%:%107=53%:%
%:%108=54%:%
%:%109=55%:%
%:%110=56%:%
%:%111=57%:%
%:%112=58%:%
%:%113=59%:%
%:%114=60%:%
%:%115=61%:%
%:%116=62%:%
%:%117=63%:%
%:%118=64%:%
%:%119=65%:%
%:%120=66%:%
%:%121=67%:%
%:%122=68%:%
%:%123=69%:%
%:%124=70%:%
%:%125=71%:%
%:%126=72%:%
%:%127=73%:%
%:%128=74%:%
%:%129=75%:%
%:%130=76%:%
%:%131=77%:%
%:%132=78%:%
%:%133=79%:%
%:%134=80%:%
%:%135=81%:%
%:%136=82%:%
%:%137=83%:%
%:%138=84%:%
%:%139=85%:%
%:%140=86%:%
%:%141=87%:%
%:%142=88%:%
%:%143=89%:%
%:%144=90%:%
%:%145=91%:%
%:%146=92%:%
%:%147=93%:%
%:%148=94%:%
%:%149=95%:%
%:%150=96%:%
%:%151=97%:%
%:%152=98%:%
%:%153=99%:%
%:%154=100%:%
%:%155=101%:%
%:%156=102%:%
%:%157=103%:%
%:%158=104%:%
%:%159=105%:%
%:%160=106%:%
%:%161=107%:%
%:%162=108%:%
%:%163=109%:%
%:%164=110%:%
%:%165=111%:%
%:%166=112%:%
%:%167=113%:%
%:%168=114%:%
%:%169=115%:%
%:%170=116%:%
%:%171=117%:%
%:%172=118%:%
%:%173=119%:%
%:%174=120%:%
%:%175=121%:%
%:%176=122%:%
%:%177=123%:%
%:%179=125%:%
%:%180=125%:%
%:%181=126%:%
%:%183=128%:%
%:%184=129%:%
%:%185=130%:%
%:%186=131%:%
%:%187=132%:%
%:%188=133%:%
%:%189=134%:%
%:%190=135%:%
%:%191=136%:%
%:%192=137%:%
%:%193=138%:%
%:%194=139%:%
%:%195=140%:%
%:%196=141%:%
%:%197=142%:%
%:%198=143%:%
%:%199=144%:%
%:%200=145%:%
%:%201=146%:%
%:%202=147%:%
%:%203=148%:%
%:%204=149%:%
%:%205=150%:%
%:%206=151%:%
%:%207=152%:%
%:%208=153%:%
%:%209=154%:%
%:%210=155%:%
%:%211=156%:%
%:%212=157%:%
%:%213=158%:%
%:%214=159%:%
%:%215=160%:%
%:%216=161%:%
%:%217=162%:%
%:%218=163%:%
%:%219=164%:%
%:%220=165%:%
%:%221=166%:%
%:%222=167%:%
%:%223=168%:%
%:%224=169%:%
%:%226=172%:%
%:%227=172%:%
%:%228=173%:%
%:%230=175%:%
%:%231=176%:%
%:%232=177%:%
%:%233=178%:%
%:%234=179%:%
%:%235=180%:%
%:%236=181%:%
%:%237=182%:%
%:%238=183%:%
%:%239=184%:%
%:%240=185%:%
%:%241=186%:%
%:%242=187%:%
%:%243=188%:%
%:%244=189%:%
%:%245=190%:%
%:%246=191%:%
%:%247=192%:%
%:%248=193%:%
%:%249=194%:%
%:%250=195%:%
%:%252=197%:%
%:%253=197%:%
%:%254=198%:%
%:%256=199%:%
%:%257=200%:%
%:%260=202%:%
%:%261=203%:%
%:%262=204%:%
%:%263=205%:%
%:%264=206%:%
%:%265=207%:%
%:%266=208%:%
%:%267=209%:%
%:%268=210%:%
%:%269=211%:%
%:%270=212%:%
%:%271=213%:%
%:%272=214%:%
%:%273=215%:%
%:%274=216%:%
%:%275=217%:%
%:%276=218%:%
%:%277=219%:%
%:%278=220%:%
%:%279=221%:%
%:%280=222%:%
%:%281=223%:%
%:%282=224%:%
